Versioned data: why it’s needed and how it can be achieved (easily and cheaply)

### 2017-08-03 ms.tex
more writing

\subsection{Allowing for one or more data contributers}

@@

\section{Discussion}

Many of the key roadblocks preventing a switch from a static to a dynamic data world, were technological: in the past it took great deal of money and expertise to set up a VDD system. The proliferation of cloud--based tools and open--source software have now reduced these roadblocks considerably.  We argue that by linking together the tools described above, researches can now produce, curate and distribute versioned data much more easily and cheaply than in the past.

>>>>

\subsection{Potential for collaboration: allowing for one or more data contributors}

@@

\section{Discussion}
% General problem. An example of solution. Key features

The problem of tracking data through time and versions is likely to be widespread. There are many alternate solutions, with associated features and drawbacks.  The current structure of scientific research is very distributed, with research groups across the world working on the same question.  Moreover at a time of funding scarcity, many world-class research groups do not have excess funds to hire and support technology specialists.  As such we argue that there is a niche for a easy, cheap, and flexible VDD system.

Many of the key roadblocks preventing a switch from a static to a dynamic data world, were technological: in the past it took great deal of money and expertise to set up a VDD system. The proliferation of cloud--based tools and open--source software have now reduced these roadblocks considerably.  We argue that by linking together the tools described above, researchers can now produce, curate and distribute versioned data much more easily and cheaply than in the past.

The key features of a VDD system that are already possible are a versioning system to communicate small and large changes to users, both point-and-click and code-based access to all versions, reliable distribution to many users, and stable, organized DOIs.  Moreover, it is relatively easy to update and add new versions.  Technology is moving forward rapidly and so it is very likely that the particular tools we describe above will add features and be even easier to use.  But nonetheless, workable systems are already possible.
